Fusion Moves for Correlation Clustering

### 2014-11-06 paper/egpaper_for_review.tex
energy based hc section
wip

Hierarchical clustering can be used to find approximate
solutions for correlation clustering.
In each step, the edge with the highest weight $w$ is
contracted (red edges in fig. ~\ref{fig:hc_alg}).
Doing so, parallel edges edges can occur.
Whenever there are multiple edges between 
a pair of nodes, these edges are merged into a single edge
by summing up their weights.
The algorithm stops if the highest edge weight is
smaller or equal to zero  (green edge in fig. ~\ref{fig:hc_alg}). Any further edge
contraction leads to worse energies.

Given the intrinsic greediness of hierarchical clustering, 
we do not expect very good solutions, but still a good starting 
point for move making algorithm as CGC \cite{beier_2014_cvpr}.
Therefore we propose to initialize  CGC with EBHC
and hope speedup of CGC.

>>>>

Agglomerative hierarchical clustering (HC) is widely used
in graph / energy segmentation
\cite{arbelaez_2006}.
Hierarchical clustering is fast, and 
due to the agglomeration of edge weights, 
hierarchical clustering is robust against noise.

HC can be used to find approximate
solutions for correlation clustering.
In each step, the edge with the highest weight $w$ is
contracted (red edges in fig. ~\ref{fig:hc_alg}).
Doing so, parallel edges edges can occur.
Whenever there are multiple edges between 
a pair of nodes, these edges are merged into a single edge
by summing up their weights.
The algorithm stops if the highest edge weight is
smaller or equal to zero  (green edge in fig. ~\ref{fig:hc_alg}). Any further edge
contraction leads to worse energies.

Given the intrinsic greediness of hierarchical clustering, 
we do not expect very good solutions, but still a good starting 
point for move making algorithm as CGC \cite{beier_2014_cvpr}.
Therefore we propose to initialize  CGC with EBHC
and hope to speedup of CGC with this starting point.
